Probabilistic Inference of Basic Stellar Parameters:\\ Application to Flickering Stars \altaffilmark{\titledag}

### 2016-01-26 version1.0/manuscript.tex
changes to figures, tables and equations

The two models we use to describe the relationships between $F_8$, \logg\ and
\rhostar\ are
\begin{equation}
% 	\log_{10}(\rho_\star) \sim \mathcal{N} \left(\mu = \alpha + \beta
% 	\log_{10}(F_8), \sigma = \sqrt{\sigma_{\rho}^2 + \gamma F_8}\right),
	\log_{10}(\rho_\star) \sim \mathcal{N} \left(\mu = \alpha_\rho +
    \beta_\rho \log_{10}(F_8), \sigma^2 = \sigma_\rho^2 \right),
\end{equation}
\label{eq:rho}
and
\begin{equation}
% 	\log_{10}(g) \sim \mathcal{N}\left(\mu = \delta + \epsilon \log_{10}(F_8),
% 	\sigma = \sqrt{\sigma_g^2 + \zeta F_8}\right).
	\log_{10}(g) \sim \mathcal{N} \left(\mu = \alpha_g + \beta_g
    \log_{10}(F_8), \sigma^2 = \sigma_g^2 \right).
\end{equation}
\label{eq:logg}
The free parameters of the two models are $\alpha_\rho$, $\beta_\rho$,
$\sigma_\rho$, $\alpha_g$, $\beta_g$ and $\sigma_g$.
These relations are Gaussian distributions with means given by the equation of
a straight line, and standard deviations which describe the intrinsic scatter
about the mean.

We also tested a model in which the additional scatter depends on flicker
itself, defined as
\begin{equation}
	\log_{10}(\rho_\star) \sim \mathcal{N} \left(\mu = \alpha_\rho +
    \beta_\rho \log_{10}(F_8), \sigma = \sqrt{\sigma_{\rho}^2 +
    \gamma_\rho F_8}\right),
\end{equation}
\label{eq:rho2}
for flicker vs $\rho_\star$ and similarly for \logg.
This model allowed us to determine whether there the magnitude of additional
scatter varied as a function of \logg or \rhostar.
In other words, whether flicker was a better proxy for \logg\ or \rhostar\ for
either dwarf or giant stars.
We found that the maximum {\it a-posteriori} values for the $\gamma$
parameters were consistent with zero: $\gamma_{rho} = 0.006 \pm 0.02, \gamma_g
= -0.01 \pm\ 0.01$, and interpret this as evidence for a constant intrinsic
scatter level across evolutionary stages.

@@

We tested a likelihood function which accounts for 2-D uncertainties but does
not allow the intrinsic scatter to be a function of the dependent or
independent variables.
For the relation between flicker and \rhostar, this likelihood function can be
written as
\begin{eqnarray}
	& p(\rho_*| F_8, \alpha, \beta, \sigma_{\rho}) =  \\ \nonumber
						      & \exp \left[-\frac{1}{2}
		\sum_{n=1}^N \frac{[F_{8n}-(\alpha + \beta \rho_{*n})]^2}
	{\left[\beta \sigma_{F8, n}^2 + (\sigma_{\rho *, n}
	+ \sigma_{\rho})^2\right]}\right]
	\\ \nonumber
	& + \beta^2 \sigma_{F8, n}^2 + (\sigma_{\rho *, n} + \sigma_{\rho})^2,
\end{eqnarray}
\label{eq:likelihood}
and similarly for \logg.
We found that the posterior PDFs for the model parameters obtained using this
likelihood function were consistent with those obtained using a model that
only accounts for the uncertainties on the flicker measurements, so instead
used a standard Gaussian likelihood function $(-1/2\chi^2)$ in our analysis.
% Since the uncertainties on flicker were significantly larger than those on
% \logg or \rhostar, regression was performed with flicker as the dependent
% variable.

We used uniform priors over all our parameters:
\begin{eqnarray}
	&	\alpha, \beta, \delta, \epsilon
	\sim U(-10:10) \\ \nonumber
 	&	\sigma_{rho}, \gamma, \sigma_g, \zeta  \sim U(-100:100).
\end{eqnarray}
\label{eq:priors}

@@

%%% rhostar plot
\begin{figure}
\begin{center}
% \includegraphics[width=8.4cm,angle=0,clip=true]{../figs/rho_vs_flicker.pdf}
\includegraphics[width=8.4cm,angle=0,clip=true]{new_rho.pdf}
\caption{
Stellar density vs. flicker.
This figure shows the model, conditioned on the data.
The solid black line shows the highest-likelihood sample, and the pink shaded
regions show the 1 and 2$\sigma$ confidence intervals.}
\label{fig:rhostar}
\end{center}
\end{figure}

%%% logg plot
\begin{figure}
\begin{center}
% \includegraphics[width=8.4cm,angle=0,clip=true]{../figs/logg_vs_flicker.pdf}
\includegraphics[width=8.4cm,angle=0,clip=true]{new_logg.pdf}
\caption{
$\log(g)$ vs. flicker.
As in \ref{fig:rhostar} this figure shows the model, conditioned on the data.
The solid black line shows the highest-likelihood sample, and the blue shaded
regions show the 1 and 2$\sigma$ confidence intervals.}
\label{fig:logg}
\end{center}
\end{figure}

\begin{table}
\caption{Highest-likelihood parameter values with 16th and 84th
	percentile uncertainties.}
\begin{tabular}{lccc}
\hline\hline
Parameter & Variable dispersion model & Constant dispersion model \\
    \hline
$\alpha$ &    2.358$_{-0.04}^{+0.08}$ &       2.191$_{-0.05}^{+0.05}$  \\
$\beta$ &    -1.79$_{-0.03}^{+0.04}$ &        -1.724$_{-0.03}^{+0.03}$ \\
$\sigma_{rho}$ &    0.015$_{-0.04}^{+0.08}$ &   0.085$_{-0.05}^{+0.05}$  \\
$\gamma$ &    -0.0$_{-0.04}^{+0.08}$ & \\
\hline
$\delta$ &    5.535$_{-0.07}^{+0.07}$ &      5.739$_{-0.03}^{+0.03}$  \\
$\epsilon$ &    -1.005$_{-0.04}^{+0.03}$ &   -1.095$_{-0.02}^{+0.01}$ \\
$\sigma_g$ &    0.168$_{-0.07}^{+0.07}$ &    0.015$_{-0.03}^{+0.03}$  \\
$\zeta$ &    -0.014$_{-0.07}^{+0.07}$ & \\
    \hline
\end{tabular}
\end{table}
\label{tab:results}

@@

We have recalibrated the relation between short timescale brightness
fluctuations in the {\it Kepler} light curves of stars (flicker) with both
stellar density and surface gravity, whilst including parameters to describe
the intrinsic scatter in these relationships.
We included both an additive variance term {\it and} a term that allows for
some abscissa-dependent variance, presented in table \ref{tab:table}.
The additive terms, $\sigma_\rho$ and $ \sigma_g$ are both non-zero,
suggesting that there {\it is} an additional source of scatter in the
relations, not accounted for by the observational uncertainties alone.
This is either caused by intrinsic scatter in the physical relationship
between flicker and density and \logg, produced by some physical process that
is not accounted for in the model, or by an underestimation of the
observational uncertainties.
Interestingly, the abscissa-dependent variances, $\gamma$ and $\zeta$ are both
less than zero.
This indicates that the intrinsic scatter either decreases with increasing
flicker and decreasing stellar density and surface gravity, or that the
uncertainty underestimation is more severe for the giant stars.
Regardless of the cause of the additional scatter needed to describe the
relations between these parameters, the conclusions of this study are the same.
Firstly, naively modelling the relationship between flicker and surface
gravity or stellar density, or any other stochastic relationship
deterministically, will lead to an underprediction of the uncertainties in
dependent variable.
Secondly, we find marginal evidence for decreased scatter at higher surface
gravities and densities, i.e. the relations between flicker, surface gravity
and stellar density are valid for dwarfs and giants alike, despite the fact
that observational uncertainties tend to be larger for dwarfs.

This is a simple `fitting a line to data' exercise, however it continues the
discussion of probabilistic modelling that is an active topic within the
fields of exoplanet and stellar astronomy.
We used Hierarchical Bayesian Modelling (HBM) to constrain the intrinsic
scatter in the relationship between flicker, surface gravity and density.
We also included the effects of the non-negligable two-dimensional observational
uncertainties by marginalizing over latent variables using importance sampling.
% Although none of these methods, nor the data used here are new taken alone,
% we use the example of flicker to demonstrate the ideas and the importance of
% probabilistic, hierarchical inference.
Relationships between astronomical parameters are almost always
non-deterministic; an element of stochasticity effects the physical parameters
of stars so one can never perfectly predict $y$ given an observation of $x$.
We advocate a probabilistic approach in both the `fitting the model to data'
step, {\it and} when using an empirically calibrated model to predict
parameter values.
The fitting stage benefits because if the relationships between parameters are
falsely assumed to be deterministic, they will be skewed by data points with
unrepresentative uncertainties.
The prediction stage benefits from the stochastic treatment both because a
probability distribution is in many ways more representative of an observation
than a point estimate, and because posterior PDF samples can be used in
subsequent studies (provided the prior used during the fitting process is
described).

We provide posterior PDF samples and the code used in this project at
\url{https://github.com/RuthAngus/flicker}.
Whenever a prediction for the surface gravity or density of a star is required,
for a given estimate of flicker, we recommend using these posterior samples
within the calculation of $\rho_{*}$ or $\log(g)$ and its (Monte Carlo)
uncertainty.
These posterior samples will naturally fold-in the covariances between
parameters.
Simple analytical uncertainty propagation is only valid when uncertainties are
Gaussian and uncorrelated which is rarely true and certainly not the case when
the model is a straight line (the slope and intercept are alway correlated).
A flicker value with uncertainties (or even better: posterior PDF
samples), input into our model will result in a probability distribution over
stellar densities or surface gravities which reflects both the uncertainties
on the flicker measurement, the uncertainties on the model parameters {\it and}
the intrinsic scatter in the flicker-$\rho_{*}$-$\log(g)$ relations.

@@

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Andrieu \& Roberts}{2009}]{andrieu:2009}
Andrieu, C., \& Roberts, G.~O., Ann. Statist., 2, 695
\bibitem[\protect\citeauthoryear{Angus et al.}{2015}]{angus:2015}
Angusr, R., Aigrain, S., Foreman-Mackey, D. \& McQuillan, A., 2015, MNRAS,
450, 1787
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien,
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Chaplin et al.}{2014}]{chaplin:2014}
Chaplin, W.~J., Basu, S., Huber, D. et al., 2014, ApJS, 210, 1
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014}
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781,
124
\bibitem[\protect\citeauthoryear{Foreman-Mackey et al.}{2014}]
{foreman-mackey:2014} Foreman-Mackey, D., Hogg, D.~W. \& Morton, T.~D., 2014,
ApJ, 795, 64
\bibitem[\protect\citeauthoryear{Fox}{1997}]{fox:1997}
Fox, J., 1997, Applied Regression Analysis, Linear Models, and Related Methods
(Thousand Oaks:Sage Publications, Inc.)
\bibitem[\protect\citeauthoryear{Fuller}{1987}]{fuller:1987}
Fuller, W.~A., 1987, Wiley Series in Probability and Mathematical Statistics
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010}]{hogg:2010}
Hogg, D.~W., Myers, A.~D. \& Bovy, J., 2010, ApJ, 725,
2166
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010b}]{hogg:2010b}
Hogg, D.~W., Bovy, J. \& Lang, D., 2010
\bibitem[\protect\citeauthoryear{Huber et al.}{2013}]{huber:2013}
Huber, D., Chaplin, W.~J., Christensen-Dalsgaard, J. et al., 2013, ApJ, 767,
127
\bibitem[\protect\citeauthoryear{Kelly}{2007}]{kelly:2007} Kelly, B.~C., 2007,
ApJ, 665, 1489
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014}
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Rogers}{2015}]{rogers:2015}
Rogers, L.~A., 2015, ApJ, 801, 41
\bibitem[\protect\citeauthoryear{Seager \& Mall\'{e}n-Ornelas}{2003}]
{seager:2003}Seager, S., \& Mall\'{e}n-Ornelas, G., 2003, ApJ, 585, 1038
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015}
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted
(astro-ph:1504.07557)
\end{thebibliography}

>>>>

The two models we use to describe the relationships between $F_8$, \logg\ and
\rhostar\ are
\begin{equation}
% 	\log_{10}(\rho_\star) \sim \mathcal{N} \left(\mu = \alpha + \beta
% 	\log_{10}(F_8), \sigma = \sqrt{\sigma_{\rho}^2 + \gamma F_8}\right),
	\log_{10}(F_8) \sim \mathcal{N} \left(\mu = \alpha_\rho +
    \beta_\rho \log_{10}(\rho_\star), \sigma^2 = \sigma_\rho^2 \right),
\end{equation}
\label{eq:rho}
and
\begin{equation}
% 	\log_{10}(g) \sim \mathcal{N}\left(\mu = \delta + \epsilon \log_{10}(F_8),
% 	\sigma = \sqrt{\sigma_g^2 + \zeta F_8}\right).
	\log_{10}(F_8) \sim \mathcal{N} \left(\mu = \alpha_g + \beta_g
    \log_{10}(g), \sigma^2 = \sigma_g^2 \right).
\end{equation}
\label{eq:logg}
The free parameters of the two models are $\alpha_\rho$, $\beta_\rho$,
$\sigma_\rho$, $\alpha_g$, $\beta_g$ and $\sigma_g$.
These relations are Gaussian distributions with means given by the equation of
a straight line, and standard deviations which describe the intrinsic scatter
about the mean.

We also tested a model in which the additional scatter depends on flicker
itself, defined as
\begin{equation}
	\log_{10}(F_8) \sim \mathcal{N} \left(\mu = \alpha_\rho +
    \beta_\rho \log_{10}(\rho_\star), \sigma = \sqrt{\sigma_{\rho}^2 +
    \gamma_\rho F_8}\right),
\end{equation}
\label{eq:rho2}
for flicker vs $\rho_\star$ and similarly for \logg.
This model allowed us to determine whether there the magnitude of additional
scatter varied as a function of flicker.
In other words, whether flicker was a better proxy for \logg\ or \rhostar\ for
either dwarf or giant stars.
We found that the maximum {\it a-posteriori} values for the $\gamma$
parameters were consistent with zero: $\gamma_{rho} = 0.006 \pm 0.02, \gamma_g
= -0.01 \pm\ 0.01$, and interpret this as evidence for a constant intrinsic
scatter level across evolutionary stages.

@@

We used a likelihood function which accounts for 2-D uncertainties but does
not allow the intrinsic scatter to be a function of the dependent or
independent variables.
For the relation between flicker and \rhostar, this likelihood function can be
written as
\begin{eqnarray}
	& p(F_8|\rho_\star, \alpha, \beta, \sigma_{\rho}) =  \\ \nonumber
						      & \exp \left[-\frac{1}{2}
		\sum_{n=1}^N \frac{[F_{8n}-(\alpha + \beta \rho_{*n})]^2}
	{\left[\beta \sigma_{F8, n}^2 + (\sigma_{\rho *, n}
	+ \sigma_{\rho})^2\right]}\right]
	\\ \nonumber
	& + \beta^2 \sigma_{F8, n}^2 + (\sigma_{\rho *, n} + \sigma_{\rho})^2,
\end{eqnarray}
\label{eq:likelihood}
and similarly for \logg.
We found that the posterior PDFs for the model parameters obtained using this
likelihood function were consistent with those obtained using a model that
only accounts for the uncertainties on the flicker measurements.
Accounting for uncertainties on $y$ {\it and} $x$ is therefore not essential
in this case but still good practise and will, in general, produce more
accurate model parameters and uncertainties.

% so instead
% used a standard Gaussian likelihood function $(-1/2\chi^2)$ in our analysis.
% Since the uncertainties on flicker were significantly larger than those on
% \logg or \rhostar, regression was performed with flicker as the dependent
% variable.

We used the uninformative prior for the parameters of a straight line with
unknown variance, outlined in \citet{vanderplas},
\begin{equation}
P(\alpha, \beta, \sigma) \propto \frac{1}{\sigma} \left( 1 + \beta^2
\right)^{-3/2}.
\end{equation}
\label{eq:priors}

@@

%%% rhostar plot
\begin{figure}
\begin{center}
\includegraphics[width=8.4cm,angle=0,clip=true]{flicker_vs_rho.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{../figs/rho_vs_flicker.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{new_rho.pdf}
\caption{
Stellar density vs. flicker.
This figure shows the model, conditioned on the data.
The solid black line shows the model with the parameter values quoted in the
text.
The solid pink lines show the 1$\sigma$ region where the extra scatter is not
included and the pink shaded regions show the 1 and 2$\sigma$ regions with the
additional scatter.}
\label{fig:rhostar}
\end{center}
\end{figure}

%%% logg plot
\begin{figure}
\begin{center}
\includegraphics[width=8.4cm,angle=0,clip=true]{flicker_vs_logg.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{../figs/logg_vs_flicker.pdf}
% \includegraphics[width=8.4cm,angle=0,clip=true]{new_logg.pdf}
\caption{
$\log(g)$ vs. flicker.
As in \ref{fig:rhostar} this figure shows the model, conditioned on the data.
The solid black line shows the model with the parameter values quoted in the
text.
The solid blue lines show the 1$\sigma$ region where the extra scatter is not
included and the blue shaded regions show the 1 and 2$\sigma$ regions with the
additional scatter.}
\label{fig:logg}
\end{center}
\end{figure}

\begin{table}
\begin{center}
\caption{Median parameter values with 16th and 84th
	percentile uncertainties.}
\begin{tabular}{lcc}
\hline\hline
Parameter & Median value \\
    \hline
$\alpha_\rho$   &    1.315$\pm 0.008$   \\
$\beta_\rho$    &    -0.526$\pm 0.009$   \\
$\sigma_\rho$   &    0.065$\pm 0.003$   \\
% 1.31476104613 0.00759733599155 0.00767814819025
% -0.525867117083 0.00913323668806 0.00926420817321
% 0.0650160215492 0.00300880167448 0.00288553857806
\hline
$\alpha_g$      &    4.90$\pm 0.05$   \\
$\beta_g$       &   -0.83$\pm 0.01$   \\
$\sigma_g$      &    0.056$\pm 0.003$   \\
% 4.90451472909 0.0514398889837 0.0509386027456
% -0.8252952869 0.0130730719222 0.0131097233196
% 0.0565263079576 0.00279179051697 0.00271277097572
    \hline
\end{tabular}
\end{center}
\end{table}
\label{tab:results}

@@

We have recalibrated the relation between short timescale brightness
fluctuations in the {\it Kepler} light curves of stars (flicker) with both
stellar density and surface gravity, whilst including parameters to describe
the intrinsic scatter in these relationships, presented in table
\ref{tab:results}.
The additive terms, $\sigma_\rho$ and $ \sigma_g$ are both non-zero,
suggesting that there {\it is} an additional source of scatter in the
relations, not accounted for by the observational uncertainties alone.
This is either caused by intrinsic scatter in the physical relationship
between flicker and density and \logg, produced by some physical process that
is not accounted for in the model, or by an underestimation of the
observational uncertainties.
We also tested a model with both an additive variance term {\it and} a term
that included flicker-dependent variance.
We found that the need for additional flicker-dependent variance was not
supported by the data, indicating that the intrinsic scatter in the relations
between flicker, \logg\ and \rhostar\ does not depend on evolutionary state.

This is a simple `fitting a line to data' exercise, however it continues the
discussion of probabilistic modelling that is an active topic within the
fields of exoplanet and stellar astronomy.
We used Hierarchical Bayesian Modelling (HBM) to constrain the intrinsic
scatter in the relationship between flicker, surface gravity and density and
included the effects of the non-negligable two-dimensional observational
uncertainties.
% Although none of these methods, nor the data used here are new taken alone,
% we use the example of flicker to demonstrate the ideas and the importance of
% probabilistic, hierarchical inference.
Relationships between astronomical parameters are almost always
non-deterministic; an element of stochasticity effects the physical parameters
of stars so one can never perfectly predict $y$ given an observation of $x$.
We advocate a probabilistic approach in both the `fitting the model to data'
step, {\it and} when using an empirically calibrated model to predict
parameter values.
The fitting stage benefits because if the relationships between parameters are
falsely assumed to be deterministic, they will be skewed by data points with
unrepresentative uncertainties.
The prediction stage benefits from the stochastic treatment both because a
probability distribution is in many ways more representative of an observation
than a point estimate, and because posterior PDF samples can be used in
subsequent studies (provided the prior used during the fitting process is
described).

We provide posterior PDF samples and the code used in this project at
\url{https://github.com/RuthAngus/flicker}.
Whenever a prediction for the surface gravity or density of a star is required,
for a given estimate of flicker, we recommend using these posterior samples
within the calculation of \rhostar or \logg\ and its (Monte Carlo)
uncertainty.
These posterior samples will naturally fold in the covariances between
parameters.
Simple analytical uncertainty propagation is only valid when uncertainties are
Gaussian and uncorrelated which is rarely true and certainly not the case when
the model is a straight line (the slope and intercept are alway correlated).
A flicker value with uncertainties (or even better: posterior PDF
samples), input into our model will result in a probability distribution over
stellar densities or surface gravities which reflects both the uncertainties
on the flicker measurement, the uncertainties on the model parameters {\it and}
the intrinsic scatter in the flicker-\rhostar-\logg\ relations.

@@

% #####################################################################
%% Bibliography
\begin{thebibliography}{99}
\bibitem[\protect\citeauthoryear{Andrieu \& Roberts}{2009}]{andrieu:2009}
Andrieu, C., \& Roberts, G.~O., Ann. Statist., 2, 695
\bibitem[\protect\citeauthoryear{Angus et al.}{2015}]{angus:2015}
Angusr, R., Aigrain, S., Foreman-Mackey, D. \& McQuillan, A., 2015, MNRAS,
450, 1787
\bibitem[\protect\citeauthoryear{Bastien et al.}{2013}]{bastien:2013} Bastien,
F. A., Stassun, K. G., Basri, G. \& Pepper, J., 2013, Nature, 500, 427
\bibitem[\protect\citeauthoryear{Chaplin et al.}{2014}]{chaplin:2014}
Chaplin, W.~J., Basu, S., Huber, D. et al., 2014, ApJS, 210, 1
\bibitem[\protect\citeauthoryear{Cranmer et al.}{2014}]{cranmer:2014}
Cranmer, S. R., Bastien, F. A., Stassun, K. G. \& Saar, S. H., 2014, ApJ, 781,
124
\bibitem[\protect\citeauthoryear{Foreman-Mackey et al.}{2014}]
{foreman-mackey:2014} Foreman-Mackey, D., Hogg, D.~W. \& Morton, T.~D., 2014,
ApJ, 795, 64
\bibitem[\protect\citeauthoryear{Fox}{1997}]{fox:1997}
Fox, J., 1997, Applied Regression Analysis, Linear Models, and Related Methods
(Thousand Oaks:Sage Publications, Inc.)
\bibitem[\protect\citeauthoryear{Fuller}{1987}]{fuller:1987}
Fuller, W.~A., 1987, Wiley Series in Probability and Mathematical Statistics
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010}]{hogg:2010}
Hogg, D.~W., Myers, A.~D. \& Bovy, J., 2010, ApJ, 725,
2166
\bibitem[\protect\citeauthoryear{Hogg et al.}{2010b}]{hogg:2010b}
Hogg, D.~W., Bovy, J. \& Lang, D., 2010
\bibitem[\protect\citeauthoryear{Huber et al.}{2013}]{huber:2013}
Huber, D., Chaplin, W.~J., Christensen-Dalsgaard, J. et al., 2013, ApJ, 767,
127
\bibitem[\protect\citeauthoryear{Kelly}{2007}]{kelly:2007} Kelly, B.~C., 2007,
ApJ, 665, 1489
\bibitem[\protect\citeauthoryear{Kipping et al.}{2014}]{kipping:2014}
Kipping, D.~M., Bastien, F.~A., Stassun, K.~G., Chaplin, W.~J., Huber, D. \&
Buchhave, L.~A., 2014, ApJ, 785, 32
\bibitem[\protect\citeauthoryear{Rogers}{2015}]{rogers:2015}
Rogers, L.~A., 2015, ApJ, 801, 41
\bibitem[\protect\citeauthoryear{Seager \& Mall\'{e}n-Ornelas}{2003}]
{seager:2003}Seager, S., \& Mall\'{e}n-Ornelas, G., 2003, ApJ, 585, 1038
\bibitem[\protect\citeauthoryear{Wolfgang et al.}{2015}]{wolfgang:2015}
\bibitem[VanderPlas(2014)]{vanderplas}
VanderPlas, J.\ 2014, arXiv:1411.5018
Wolfgang, A., Rogers, L.~A., Ford, E.~B., 2015, ApJ, submitted
(astro-ph:1504.07557)
\end{thebibliography}
